---
title: "Epidemiological simulation report"
author: "Le CNAM, Institut Pasteur, Inserm, Université Paris-Saclay"
date: "2/10/2021"
output: pdf_document
params:
  trajmwss: NA,
  ward_names: NA,
  pop_size_P: NA,
  pop_size_H: NA,
  nVisits: NA,
  LS: NA,
  matContact: NA,
  IMMstate: NA,
  EPIstate: NA,
  clustering: NA,
  disease: NA,
  gdata: NA,
  scenarios: NA
---


```{r setup, include=FALSE}
options(tinytex.verbose = TRUE)
knitr::opts_chunk$set(echo = FALSE)
```

```{r message= FALSE, warning = FALSE}
library(mwss)
```

## Objective
Dynamic epidemiological modeling is a powerful tool to analyze the risk of pathogen persistence and spread, following an introduction in a population, as well as predicting the impact of surveillance and control strategies. In small populations such as patients and healthcare workers in healthcare settings, heterogeneity and stochasticity play fundamental roles due to the risk of super-spreading events or epidemic extinction. Epidemic models of hospital-acquired infections generally consider a unique homogeneous population and do not account for the organizational or multi-ward structure, hindering the capacity of models to capture nosocomial spread processes accurately. 

We use here a network-structured model to simulate disease spreading across wards inside a healthcare facility and test the efficacy of intervention strategies on disease control. 

## Methods
### Hospital structure and population

```{r, results='asis'}
if(!is.null(params$clustering))
cat('
This report presents synthetic results of', length(params$trajmwss), 'simulations run for an',  params$clustering, 'hospital structure including', length(params$ward_names), 'wards distributed over five buildings, and connected through healthcare workers (the structure is detailed in the following figure and table).')

if(is.null(params$clustering))
cat('
This report presents synthetic results of', length(params$trajmwss), 'simulations run for an hospital structure including', length(params$ward_names), 'wards distributed over five buildings, and connected through healthcare workers (the structure is detailed in the following figure and table).')
```

<!-- Plots: 1. connectivity plot for the network of wards // 2. Population size (patients, HCWs) -->
```{r message= FALSE, warning = FALSE}
   if(length(params$ward_names) > 1) {
      # FIX ME colors only for preprocessed test datasets
     if(identical(params$ward_names, build_network()$ward_names))
      plot_connectivity(
        matContact = params$matContact,
        size = as.numeric(params$pop_size_P) + as.numeric(params$pop_size_H),
        vertexcexrate = 3,
        vertexcol = c(rep("red",3),
                      rep("blue",4),
                      rep("white",5),
                      rep("yellow",8),
                      rep("orange",9)),
        verbose = FALSE
      ) else
      plot_connectivity(
        matContact = params$matContact,
        size = as.numeric(params$pop_size_P) + as.numeric(params$pop_size_H),
        vertexcexrate = 3,
        verbose = FALSE
      ) 
   }

  df <- data.frame(Number_of_patients = params$pop_size_P,
                 Number_of_healthcare_workers = params$pop_size_H,
                 # Daily_visits = params$nVisits,
                 Length_of_stay_in_days = round(params$LS,1), 
                 row.names = params$ward_names)
  
  colnames(df) = gsub("_", " ",colnames(df))
  
 kable(df)
                  
```

### Epidemiology: pathogen and immunity level
We simulate the diffusion of  ``r params$disease`` in a fully susceptible population (no immunity).

<!-- in a population with **no/low/high/heterogeneous** immunity/ -->

<!-- A couple of key parameters to include: -->
<!-- 1. Baseline transmissible (R0) -->
The baseline basic reproduction number (R0) considered was ``r if(params$disease == "Covid") 13 else if(params$disease == "Influenza") 1.3   # params$gdata["pconta"]*(8 * (30 / 60 / 24) * params$gdata["prev"]/params$gdata["hinc"])``.

<!-- 2. Severity (probability of developing (severe) symptoms) -->
The severity (probability of developing severe symptoms) considered is ``r params$gdata["psevPNI"]`` for individuals without any immunity (neither vaccinated nor recovered), ``r params$gdata["psevPLI"]`` for individuals with a low immunity level (considering either an old vaccine injection or recovery), and ``r params$gdata["psevPHI"]`` for individuals with a high immunity level (considering either a recent vaccine injection or recovery).

<!-- 3. Fraction of HCW and PATIENTS with low/high immunity. -->



<!-- A quick recap of the interventions assumed.  -->
### Intervention strategies
```{asis, echo = !is.null(params$scenarios)}
In this simulation, the following intervention strategies were implemented.
```

<!-- 1. confinement/contact restriction to detected patients -->

```{asis, echo = "ISO" %in% params$scenarios}
#### Confinement/contact restriction to detected patients
The risk of transmission during contacts with patients detected as infected is considered null.
```
<!-- 2. implementation of a screening area at patient admission including contact restriction/clinical examination/test -->
```{asis, echo = "SA" %in% params$scenarios}

#### Implementation of a screening area at patient admission including contact restriction, clinical examination and test
Before admission, new patients undergo a clinical examination, during which they can be tested. Symptomatic patients are always tested, and among asymptomatic or susceptible patients: 75% of patients with no vaccination or infection history, 50% of patients with old vaccination or infection history and 25% of patients with recent vaccination or infection history will undergo a test. The model considers 2 contacts of 10min with the professional in charge of admission and no contact with other patients during the admission process.
```
<!-- 3. screening of patients by implementation of tests on a random subset of patient population at regular intervals -->
```{asis, echo = "testPat" %in% params$scenarios}

#### Screening of patients by implementation of tests on a random subset of patient population at regular intervals
For patients, random testing is implemented every week in 75% of patients with no vaccination or infection history, 50% of patients with old vaccination or infection history and 10% of patients with recent vaccination or infection history.

Note that the model considers that a tested individual will not be tested again before a minimal duration fixed as the duration of the disease (eg 10 days for covid).

```
<!-- 4. screening of healthcare workers by implementation of tests on a random subset of healthcare worker population at regular intervals -->
```{asis, echo = "testProf" %in% params$scenarios}

#### Screening of healthcare workers by implementation of tests on a random subset of healthcare worker population at regular intervals
For healthcare workers, random testing is implemented every two weeks in 75% of healthcare workers with no vaccination or infection history, 50% of healthcare workers with old vaccination or infection history and 20% of healthcare workers with recent vaccination or infection history.

The model further assumes that a healthcare worker will take sick leave with 100% probability if he develops severe symptoms, 30% probability if he develops mild symptoms but is not tested or tested negative, and 50% probability if he is tested positive.

Note that the model considers that a tested individual will not be tested again before a minimal duration fixed as the duration of the disease (eg 10 days for covid).
```

```{asis, echo = is.null(params$scenarios)}
No intervention strategy was implemented. The results presented here consider a baseline scenario without any interventions.
```


<!-- A quick recap of the importation level assumed.  -->
### Level of importation


```{r results='asis', echo=FALSE}
if (params$gdata[['hinc']] == 0) {cat(paste0('In this simulation, no regular importation was implemented, incidence was set at 0. The simulations only considered an index case in ward ', params$EPIstate$ward, '.')     
)}


if (params$gdata[['hinc']] == 50/100000) {cat('In this simulation, the initial population is considered as fully susceptible. A low level of importation was considered with the incidence set at 50 cases per 100,000 persons in the incoming population.'  
)}

if (params$gdata[['hinc']] == 185/100000) {cat('In this simulation, the initial population is considered as fully susceptible. A high level of importation was considered with the incidence set at 185 cases per 100,000 persons in the incoming population.'  
)}
```

## Results

<!-- All plots from the simple version app. -->

```{r message= FALSE, warning = FALSE}

n_it <- seq(length(params$trajmwss))

# add iteration
trajmwss <- lapply(n_it, function(sim) {
  params$trajmwss[[sim]][, `:=`(iteration = sim)]
  params$trajmwss[[sim]]
})

# group into unique data.table
trajmwss %<>% do.call(rbind, .)

#  cumulative daily incidence per node per iteration
trajmwss[, `:=`(incP = (sum(incPA, incPM,  incPS)),
                incH = (sum(incHA, incHM, incHS))),
         by = c("iteration", "time", "node")]

#  daily incidence per node per iteration
trajmwss[, `:=`(d_incP = diff(c(0,incP)),
                d_incH = diff(c(0,incH))),
         by = c("node", "iteration")]

#### simple_plot_peak

#  remove unused columns
peak_incidence_values <- trajmwss %>% .[, c("time","node", "iteration", "d_incP", "d_incH"), with=FALSE]

#  renames variables
setnames(peak_incidence_values, "d_incP", "Patients")
setnames(peak_incidence_values, "d_incH", "Healthcare workers")

#  remove unused columns
peak_incidence_values %<>% melt(., id.vars = c("time" , "node" , "iteration"))
# select maximal incidence in each node for each simulation
peak_incidence_values[, `:=`(maxInc = max(value)),
                      by = c("node", "variable", "iteration")]

peak_incidence_values %<>% .[, c("node", "variable", "maxInc"), with=FALSE]
peak_incidence_values %<>% unique

# calculate mean peak and sd per node over all simulations
peak_incidence_values[, `:=`(mean = mean(maxInc),
                             sd = sd(maxInc)),
                      by = c("node", "variable")]

peak_incidence_values %<>% .[, c("node", "variable","mean","sd"), with=FALSE]
peak_incidence_values %<>% unique

peak_incidence_plot <- ggplot(peak_incidence_values) +
  facet_wrap(~variable) +
  geom_col(aes(node, mean), fill = "grey", position = "dodge") +
  geom_col(data = peak_incidence_values[order(mean), tail(.SD,5), by = variable],
           aes(node, mean, fill = variable),
           position = "dodge") +
  geom_errorbar(aes(node,
                    mean,
                    ymin = ifelse((mean-sd) < 0, 0, (mean-sd)),
                    ymax = mean+sd,
                    group = variable),
                position = "dodge") +
  labs(x = "Service", y = "Peak daily incidence") +
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1, size = 5)) +
  guides(fill = "none")


### Incidence
incidence_plot_values <- trajmwss
incidence_plot_values[, `:=`(casImpP = sum(admE, admEA, admES, admIA, admIM, admIS),
                             casImpH = infHout)]

incidence_plot_values %<>% .[, c("time","node", "iteration", "casImpP", "casImpH", "infP", "infH"), with=FALSE]

incidence_plot_values[, `:=`(casImpP = c(0,diff(casImpP)),
                             casImpH = c(0,diff(casImpH)),
                             infP = c(0,diff(infP)),
                             infH = c(0,diff(infH))),
                      by = c("node", "iteration")]

incidence_plot_values[, `:=`(infections = casImpP + casImpH + infP + infH)]

incidence_plot_values %<>% .[, c("time","node", "iteration", "infections"), with=FALSE]

# incidence_plot_values %<>% melt(., id.vars = c("time" , "node" , "iteration"))

incidence_plot_values[, `:=`(infections = sum(infections)),
                      by = c("time", "iteration")]

incidence_plot_values[, node := NULL]

incidence_plot_values %<>% unique

incidence_plot_values[, `:=`(mean = mean(infections),
                             sd = sd(infections),
                             yhat_lower = quantile(infections, 0.025),
                             yhat_upper = quantile(infections, 0.925)),
                      by = c("time")]

incidence_plot <- ggplot(incidence_plot_values) +
  geom_ribbon(aes(x=time, ymin = yhat_lower, ymax = yhat_upper),
              alpha = 0.3,
              na.rm = TRUE,
              fill = "#f68323") +
  geom_line(data = incidence_plot_values[iteration %in% 1:4],
            aes(x=time, y=infections, group=factor(iteration),
                color = factor(iteration)), linewidth = .2) +
  xlab("Time (day)") +
  ylab("Average daily number of cases (lines are 4 random simulations)") +
  theme(panel.background = element_rect(fill = "white", colour = "grey50")) +
  guides(color="none")

peak_incidence_plot

### Nosocomial hazard
plot_nosoHazard(
  trajmwss = params$trajmwss,
  ward_names = params$ward_names,
  pop_size_P = params$pop_size_P,
  LS = params$LS,
  matContact = params$matContact,
  layout = "with_fr", 
  vertexsize = 0.5, 
  vertexlabelsize = 0.03,
  edgearrowsize = 0.4,
  addtitle = TRUE,
  maxcolors = 5,
  verbose = FALSE
)

incidence_plot

plot_testcount(
        trajmwss = params$trajmwss,
        scale = 0,
        pop = NULL,
        iter = FALSE,
        ward = FALSE,
        daysint = 7
      ) + theme_bw()

                  
```

## Synthetic results (with 95% prediction interval)

```{r message= FALSE, warning = FALSE}
if(is.null(params$scenarios)){
def_params <- c(
"Number of nosocomial infections among professionals", 
"Number of imported infections among professionals", 
"Number of nosocomial infections among patients",
"Number of imported infections among patients",
"Number of severe cases among patients",
"Number of tests of patients",
"Number of tests of professionals",
"Maximal number of beds simultaneously under confinement",
"Maximal number of professionals simultaneously in sick leave")

key_numbers <- keyoutput(params$trajmwss,
                         scale = 0)

intervals_values <- rbind(
  key_numbers$infection$H$n_noso %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$infection$H$n_out %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$infection$P$n_noso %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$infection$P$n_intro %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$incidence$incidence[, incPS] %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$test$ntest[, nTestP] %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$test$ntest[, nTestH] %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  ifelse(!is.null(key_numbers$ISO),key_numbers$ISO$maxnISO %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling, NA),
  key_numbers$SL$maxnSL %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling
)

colnames(intervals_values)[1] <- "median"

table_params <- cbind(" " = def_params[!is.na(intervals_values[, "median"])], intervals_values[!is.na(intervals_values[, "median"]),]) %>% as.data.frame

kable(table_params)} else {
  gdata <- params$gdata
  gdata[['pISO']] = 0
  gdata[['ptestPWNI']] = 0
  gdata[['ptestPWLI']] = 0
  gdata[['ptestPWHI']] = 0
  gdata[['ptestHNI']] = 0
  gdata[['ptestHLI']] = 0
  gdata[['ptestHHI']] = 0
      
    mwssmodel <- mwss(
      params$ward_names,
      params$pop_size_P,
      params$pop_size_H,
      params$nVisits,
      params$LS,
      matContact = params$matContact,
      IMMstate = params$IMMstate,
      EPIstate = params$EPIstate,
      gdata = gdata,
      tSim =  params$trajmwss[[1]][,max(time)],
      verbose = FALSE
    )

    trajmwss_baseline <- multisim(mwssmodel, 50, params$ward_names)



def_params <- c(
"Number of nosocomial infections among professionals", 
"Number of imported infections among professionals", 
"Number of nosocomial infections among patients",
"Number of imported infections among patients",
"Number of severe cases among patients",
"Number of tests of patients",
"Number of tests of professionals",
"Maximal number of beds simultaneously under confinement",
"Maximal number of professionals simultaneously in sick leave")

key_numbers <- keyoutput(params$trajmwss,
                         scale = 0)

intervals_values <- rbind(
  key_numbers$infection$H$n_noso %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$infection$H$n_out %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$infection$P$n_noso %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$infection$P$n_intro %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$incidence$incidence[, incPS] %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$test$ntest[, nTestP] %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$test$ntest[, nTestH] %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  ifelse(!is.null(key_numbers$ISO),key_numbers$ISO$maxnISO %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling, NA),
  key_numbers$SL$maxnSL %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling
)

key_numbers <- keyoutput(trajmwss_baseline,
                         scale = 0)

intervals_values_baseline <- rbind(
  key_numbers$infection$H$n_noso %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$infection$H$n_out %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$infection$P$n_noso %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$infection$P$n_intro %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$incidence$incidence[, incPS] %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$test$ntest[, nTestP] %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  key_numbers$test$ntest[, nTestH] %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling,
  ifelse(!is.null(key_numbers$ISO),key_numbers$ISO$maxnISO %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling, NA),
  key_numbers$SL$maxnSL %>% quantile(., prob = c(0.5, 0.025, 0.975)) %>% ceiling
)

colnames(intervals_values)[1] <- "median"
colnames(intervals_values_baseline)[1] <- "median"
colnames(intervals_values_baseline) %<>% paste0(., '_baseline')

table_params <- cbind(" " = def_params[!is.na(intervals_values[, "median"])], intervals_values[!is.na(intervals_values[, "median"]),]) %>% 
 cbind(., intervals_values_baseline[!is.na(intervals_values[, "median"]),]) %>% as.data.frame

colnames(table_params) %<>% gsub("_", " ", .)
kable(table_params)
}

```


<!-- ## Limitations -->
<!-- To discuss. -->

```{asis, echo = !is.null(params$scenarios)}
We compare the results of this intervention scenario with a baseline scenario without any interventions.
```

## Appendix

<!-- Full table with parameters. -->
```{r message= FALSE, warning = FALSE}

#   c(params$gdata
def_param <-
  c(
    n_ctcH_PSA = "the daily number of contacts with professionals per patient in the screening area",
    t_ctcH_PSA = "the average duration of contact between professional and patient per day in the screening area (in days, ex: if 15 min, t_ctcH_PSA = 15/60/24)",
    n_ctcP_PSA = "the daily number of contacts with other patients per patient in the screening area",
    t_ctcP_PSA = "the average duration of contact between patients per day in the screening area (in days)",
    n_ctcH_PW = "the number of contact between professional and patient per day in the ward",
    t_ctcH_PW = "the average duration of contact between patients per day in the ward (in days)",
    n_ctcP_PW = "the number of contacts with other patients per patient per day, in the ward",
    t_ctcP_PW = "the average duration of contact between patients per day in the ward (in days)",
    n_ctcH_H = "the number of contacts with professionals per professional per day",
    t_ctcH_H = "the average duration of contact between professionals in the ward (in days)",
    t_ctcV_PW = "the average duration of contact between patients per day in the ward (in days)",
    I = "the daily incidence",
    d = "the average disease duration (in days)",
    R0 = "the basic reproduction number",
    tw = "the average number of working hours per week (in hours)",
    tSA = "the average duration (in days) before full admission (in screening area for clinical exam, administrative procedure, etc)",
    tIC = "the average duration (in days) of stay in intensive care",
    tSL = "the average duration (in days) of sick leave",
    tESL = "the average duration (in days) of extended sick leave",
    tE = "the average duration (in days) of epidemiological state E (exposed - non contagious)",
    tEA = "the average duration (in days) of epidemiological state EA (exposed - contagious pre-asymptomatic)",
    tES = "the average duration (in days) of epidemiological state ES (exposed - contagious pre-symptomatic)",
    tIA = "the average duration (in days) of epidemiological state IA (infectious asymptomatic)",
    tIM = "the average duration (in days) of epidemiological state IM (infectious with mild symptoms)",
    tIS = "the average duration (in days) of epidemiological state IS (infectious with severe symptoms)",
    tLI = "the average duration (in days) of low immunity persistence before return to non immune status",
    tHI = "the average duration (in days) of high immunity persistence before return to low immune status",
    epsPPSA = "the average infection-reducing ratio for patient infection during patient-to-patient contacts in the screening area (0 = no protection, 1 = complete protection/no infection possible)",
    epsHPSA = "the average infection-reducing ratio for patient infection during professional-to-patient contacts in the screening area (0 = no protection, 1 = complete protection/no infection possible)",
    epsHPW = "the average infection-reducing ratio for patient infection during professional-to-patient contacts in the ward (0 = no protection, 1 = complete protection/no infection possible)",
    epsPPW = "the average infection-reducing ratio for patient infection during patient-to-patient contacts in the ward (0 = no protection, 1 = complete protection/no infection possible)",
    epsVPW = "the average infection-reducing ratio for patient infection during visitor-to-patient contacts (0 = no protection, 1 = complete protection/no infection possible)",
    epsPHSA = "the average infection-reducing ratio for professional infection during patient-to-professional contacts in the screening area (0 = no protection, 1 = complete protection/no infection possible)",
    epsPHW = "the average infection-reducing ratio for professional infection during patient-to-professional contacts in the ward (0 = no protection, 1 = complete protection/no infection possible)",
    epsHHW = "the average infection-reducing ratio for professional infection during professional-to-professional contacts (0 = no protection, 1 = complete protection/no infection possible)",
    ttestSA = "the average duration (in days) of test in the screening area (from decision to test to action - such as transfer -after obtaining the test result)",
    ttestPW = "the average duration (in days) of test in the ward for patient screening (from decision to test to action - such as transfer -after obtaining the test result)",
    ttestHW = "the average duration (in days) of test for professional screening (from decision to test to action - such as sick leave -after obtaining the test result)",
    ttestsymp = "the average duration (in days) of test for symptomatic individuals (from decision to test to action - such as sick leave or transfer -after obtaining the test result)",
    tbtwtestP = "the average duration (in days) between two patient screening testing-events in the ward",
    tbtwtestH = "the average duration (in days) between two professional screening testing-events in the ward",
    tbeftestPsymp = "the average duration (in days) of symptomatic patients detection (before test)",
    tbeftestHsymp = "the average duration (in days) of symptomatic professional detection (before test)",
    psympNI = "the conditional probability to be symptomatic when non immune",
    psympLI = "the conditional probability to be symptomatic despite a low immunity",
    psympHI = "the conditional probability to be symptomatic despite a high immunity",
    psevNI = "the conditional probability to develop severe symptoms when symptomatic and non immune",
    psevLI = "the conditional probability to develop severe symptoms when symptomatic and despite a low immunity",
    psevHI = "the conditional probability to develop severe symptoms when symptomatic and despite a high immunity",
    pISO = "level of contact restrictions (confinement/quarantine/isolation) in case of positive test",
    pSL = "the probability for professional with mild symptoms of taking sick leave",
    pESL = "the probability for professional with severe symptomsof taking extended sick leave",
    pSLT = "the additional probability for professionals of taking sick leave after positive test",
    pIC = "the probability for patient with severe symptoms to be transfer in intensive care",
    pdieIC = "the probability to die in intensive care",
    pLI = "the probability to have low immunity at the admission (proportion of individuals with low immunity in the community)",
    pHI = "the probability to have high immunity at the admission (proportion of individuals with high immunity in the community)",
    hNI2LI = "the daily probability to gain low immunity when non immune",
    hLI2HI = "the daily probability to gain high immunity when having low immunity",
    rinfLI = "the average infection-reducing ratio for individuals with low immunity compared to non immune (can be interpreted as low immunity efficiency)",
    rinfHI = "the average infection-reducing ratio for individuals with high immunity compared to non immune (can be interpreted as high immunity efficiency)",
    rsymp = "the average ratio increasing or reducing the probability to develop symptoms for patients compared to general population (professionals)",
    rsev = "the average ratio increasing or reducing the probability to develop severe symptoms for symptomatic patients compared to general population (professionals)",
    rEA = "the ratio of excretion for individuals in epidemiological stage EA (exposed - contagious pre-asymptomatic)",
    rES = "the ratio of excretion for individuals in epidemiological stage ES (exposed - contagious pre-symptomatic)",
    rIA = "the ratio of excretion for individuals in epidemiological stage IA (infectious asymptomatic)",
    rIM = "the ratio of excretion for individuals in epidemiological stage IM (infectious with mild symptoms)",
    rIS = "the ratio of excretion for individuals in epidemiological stage IS (infectious with severe symptoms)",
    ptestPSAsymp = "the probability to test symptomatic patients in the screening area",
    ptestPSANI = "the probability to test non immune patients in the screening area",
    ptestPSALI = "the probability to test patients with low immunity in the screening area",
    ptestPSAHI = "the probability to test patients with high immunity in the screening area",
    ptestPWsymp = "the probability to test symptomatic patients in the ward (Diagnostic testing)",
    ptestPWNI = "the proportion of non immune patients tested during screening testing in the ward",
    ptestPWLI = "the proportion of patients with low immunity tested during screening testing in the ward",
    ptestPWHI = "the proportion of patients with high immunity tested during screening testing in the ward",
    ptestHsymp = "the probability to test symptomatic professionals (Diagnostic testing)",
    ptestHNI = "the proportion of non immune professionals tested during screening testing",
    ptestHLI = "the proportion of professionals with low immunity tested during screening testing",
    ptestHHI = "the proportion of professionals with high immunity tested during screening testing",
    senSA = "the sensibility of tests use within the screening area",
    speSA = "the specificity of tests use within the screening area",
    senW = "the sensibility of tests use for patient screening in the ward",
    speW = "the specificity of tests use for patient screening in the ward",
    senH = "the sensibility of tests use for professional screening",
    speH = "the specificity of tests use for professional screening",
    sensymp = "the sensibility of tests use for symptomatic individuals",
    spesymp = "the specificity of tests use for symptomatic individuals",
    td = "the average disease duration (in days)",
    ctcHPSA = "the average duration of contact with patients per healthcare worker per day in the screening area (in days)",
    ctcPPSA = "the average duration of contact with other patients per patient per day in the screening area (in days)",
    ctcHPW = "the average duration of contact with patients per healthcare worker per day in the ward (in days)",
    ctcPPW = "the average duration of contact with other patients per patient per day in the ward (in days)",
    ctcHH = "the average duration of contact with other healthcare workers per heathcare worker per day (in days)",
    ctcV = "the average duration of contact with visitors per patient per day in the ward (in days)",
    hinc = "the daily incidence in the community",
    prev = "the prevalence (probability to be infected at the admission)",
    pconta = "the probability of transmission per minute spent in contact",
    ptow = "the proportion of time outside of work per healthcare worker (in days)",
    psympPNI = "the conditional probability to be symptomatic when non immune for patients",
    psevPNI = "the conditional probability to develop severe symptoms when symptomatic and non immune for patients",
    psympPLI = "the conditional probability to be symptomatic despite a low immunity for patients",
    psevPLI = "the conditional probability to develop severe symptoms when symptomatic and despite a low immunity for patients",
    psympPHI = "the conditional probability to be symptomatic despite a high immunity for patients",
    psevPHI = "the conditional probability to develop severe symptoms when symptomatic and despite a high immunity for patients",
    rtE = 'the time ratio of the epidemiological state E over the whole infectious period (probability to be exposed/incubating non infectious at the admission when non susceptible)',
    rtEA = 'the time ratio of the epidemiological state EA over the whole infectious period (probability to be exposed/incubating infectious before asymptomatic form at the admission when non susceptible)',
    rtES = 'the time ratio of the epidemiological state ES over the whole infectious period (probability to be exposed/incubating infectious before symptomatic form at the admission when non susceptible)',
    rtIA = 'the time ratio of the epidemiological state IA over the whole infectious period (probability to be infectious with asymptomatic form at the admission when non susceptible)',
    rtIM = 'the time ratio of the epidemiological state IM over the whole infectious period (probability to be infectious with mild symptoms at the admission when non susceptible)',
    rtIS = 'the time ratio of the epidemiological state IS over the whole infectious period (probability to be infectious with severe symptoms at the admission when non susceptible)')


table_of_params <- data.frame(def_param = def_param[names(params$gdata)],
                              values = sapply(params$gdata, function(x){
                                if(nchar(x) > 4) 
                                  format(x, digits = 2, scientific = TRUE) else
                                    format(x, digits = 1, scientific = FALSE)}))

row.names(table_of_params) <- NULL

colnames(table_of_params) = c('Parameters definition', 'values')
library(flextable)

# table_of_params %>% regulartable %>% dim_pretty() %>% .$widths
table_of_params %>% regulartable(. , cwidth = c(5, 1)) 

                  
```
## Modelling project:
Supported by the Département d’information médicale of the Centre hospitalier Guillaume Régnier (Rennes, France), a simulation modeling project was undertaken during the 2020 pandemic to evaluate the effect of infection control protocols on SARS-CoV-2 spread in french long-term care facilities. The modeling was carried out by the French Pasteur Institute, the French Conservatoire national des Arts et métiers, and the French University of Versailles Saint-Quentin-en-Yvelines, in collaboration with the Department of Disease Control and Epidemiology of the National Veterinary Institute of Sweden. Epidemiological simulations are performed using R-based packages: mwss and SimInf. 

Results presented in this report were generated using the open source R package ‘MWSS’ which uses the Gillespie algorithm, implemented with mwss R-package. 

Note that simulations were run locally and, to deal with data confidentiality challenges, the parameters and simulations were not saved on our servers.
